---
title: "Impact and Effectiveness of Marketing Campaign of Portuguese Banking Institution"
author:  
 - Sharifovi, Dilafuruz[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    This academic paper examines the influence and effectiveness of marketing campaigns in a specific Portuguese banking institution. The research investigates how these campaigns shape customer perceptions and preferences while identifying the factors that contribute to their success. The findings demonstrate the relationship between predictor variables and the duration of marketing campaigns. A scatter plot visualizes the progression of campaigns over time, providing insights into the relationship between campaign stages and duration stages. Predicted duration values based on the regression model enable estimates for new data points, extending predictions beyond the observed samples.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->

<!-- ============================== FOOTNOTES ============================== -->

<!-- ======================================================================= -->

[^1]: 20080946, [Github Repo](https://github.com/DilafuruzSharifovi/20080946.git)

# Introduction

Portuguese banking institutions have played a vital role in supporting the country's economic development and providing a wide range of financial services to individuals, businesses, and the government. Portuguese banks have embraced various marketing channels and techniques to engage with customers, differentiate themselves from competitors, and deliver value-added experiences. These marketing campaigns are carefully crafted to communicate the institution's core values, such as trust, transparency, and personalized service. The marketing campaigns of this Portuguese banking institution often revolve around key themes such as financial literacy, convenience, and technological innovation. They strive to educate customers about financial matters, empower them to make informed decisions, and demonstrate how their products and services can simplify their financial lives. Moreover, this banking institution recognizes the importance of engaging with customers on digital platforms. They have developed a strong online presence, employing social media campaigns, email marketing, and interactive website features to foster meaningful connections with their customers. Additionally, these marketing campaigns often highlight the bank's commitment to corporate social responsibility, emphasizing initiatives that contribute to the community and promote sustainability. By aligning their brand with socially responsible causes, the bank not only strengthens its reputation but also appeals to customers who value ethical practices and social impact. Furthermore, the success of these marketing campaigns is measured through various metrics, including customer acquisition, customer retention, and brand recognition. Portuguese banking institutions invest in market research and data analysis to evaluate the effectiveness of their campaigns, making adjustments and improvements as necessary. In conclusion, marketing campaigns play a vital role in the success and growth of Portuguese banking institutions. Through innovative approaches, Portuguese banking institutions continue to drive their marketing efforts to new heights, establishing themselves as trusted financial partners within the country. I created research question with “How have the marketing campaigns of a specific Portuguese banking institution influenced customer perceptions and preferences, and what factors contribute to the effectiveness of these campaigns?“. Also, I chose the marketing campaigns of a Portuguese banking institution, the dataset has 149 observaitons and 21 variables.

# Literature Review

The crucial role of marketing campaigns in Portuguese banking institutions, as they not only raise awareness but also shape customer perceptions and preferences. These campaigns effectively communicate the bank's core values, leveraging both traditional and digital marketing channels to engage with the target audience. To inform and empower clients, themes like financial literacy, ease, and technological innovation are frequently incorporated. By embracing digital platforms, personalized marketing efforts tailored to individual preferences and needs are achieved. Additionally, highlighting corporate social responsibility initiatives strengthens the bank's reputation and appeals to socially conscious customers. Evaluating campaign success through metrics such as customer acquisition, retention, and brand recognition enables continuous improvement. This literature review provides a foundation for understanding the impact and effectiveness of marketing campaigns in Portuguese banking institutions.

@pinho:1997 the current chapter's objectives are to assess the impact of the Single European Act on the Portuguese banking sector and to examine the preparations being made by this sector for the impending arrival of the European Monetary Union (EMU). @hosein:2021 in the modern business world, marketing is a crucial component. If clients are not aware of a product, businesses cannot profit from it. A company can sell a product using a variety of mediums. These consist of telephone calls, social media advertisements, and campaigns. @vongchalerm:2022 the Portuguese are using advanced technologies for the marketing of their products and services in an effort to increase their market share through machine learning techniques. Portuguese banks are utilizing machine learning techniques to analyze client behavior because it is crucial to the decision-making process. @al:2013 the marketing campaigns of banking institutions are crucial to their success. Phone campaigns were used for marketing campaigns. The behavior of customers is heavily influenced by phone calls. The purpose of this paper is to propose neural networks for evaluating bank marketing. @chlebus:2020 nowadays, marketing methods develop quickly as businesses look for ways to improve campaign performance while effectively utilizing their limited resources. In an effort to better serve their increasingly demanding customers, more businesses are turning to marketing. Instead than running large-scale ads, they frequently build relationships with clients to win their loyalty. This is the rationale behind why direct marketing is significant today. @ejaz:2016 banks employ marketing techniques to promote client investment subscriptions. This tactic thus improves client retention. Telemarketing is one such sales method. Banks use phone calls to solicit investments and boost business earnings. Although this approach is effective, more may be done to increase earnings.

# Data Statistics 

Important insights are presented by the statistical analysis of the provided table. The average number of campaigns per client is 1.47, with a moderate level of variability indicated by a standard deviation of 0.73. The consumer price index remains constant at 93.99 throughout the dataset. Interactions with clients have an average duration of 269.17 seconds, but exhibit high variability with a standard deviation of 233.15 seconds. The employment variation rate remains stable at 1.10. Interestingly, the majority of clients' most recent campaign contact appears to have been 999.00 days ago, indicating a lack of current engagements. The dataset can be understood and analyzed with the help of these statistics.


```{r code_chunk_name, echo = FALSE}
library(tidyverse)
library(here)
survey <- read_csv(here("data/Bank.csv"))
```

```{r, echo=FALSE}
library(xtable)
library(summarytools)
st_options(lang = "en")
```

```{r results='asis', echo=FALSE}
survey %>%
  select("duration", "campaign", "emp.var.rate", "pdays", "cons.price.idx") %>%
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>%
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>%
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```

# Methods and Data Analysis

## Predictor Variable Anaylsis: The Main Factors Affecting Marketing
(Figure \@ref(fig:predictor))
These coefficients indicate the impact of the employment variation rate on the effectiveness of the marketing campaign.The efficiency of the campaign is thought to decline when the employment variations rate rises, according to a bigger negative coefficient. When economic instability or uncertainty is present, such as when the employment variation rate is high, customers may be less receptive to marketing efforts and more careful with their spending. On the other hand, when the employment variation rate is low, indicating a stable job market, consumers may be more confident in their financial situation and more receptive to marketing messages. 


```{r predictor, fig.align='center', fig.cap='Predictor Variables', results='asis', echo=FALSE}
# Load the dataset
dataset <- read.csv("C:/Users/MSI/Desktop/20080946/data/Bank.csv")

# Perform multiple linear regression
model <- lm(`duration` ~ `campaign` + `cons.price.idx` + `emp.var.rate`, data = dataset)

# Create a bar plot of regression coefficients
coefficients <- coef(model)
predictor_names <- c("campaign", "cons.price.idx", "emp.var.rate")
coefficients_df <- data.frame(Predictor = predictor_names, Coefficient = coefficients[-1])

# Sort the coefficients by magnitude
coefficients_df <- coefficients_df[order(abs(coefficients_df$Coefficient), decreasing = TRUE), ]

# Create the bar plot
barplot(coefficients_df$Coefficient, names.arg = coefficients_df$Predictor,
        xlab = "Predictor Variables", ylab = "Coefficient",
        main = "Factors Affecting Marketing", col = "steelblue")

# Add a horizontal line at zero for reference
abline(h = 0, col = "red", lty = 2)
```

(Figure \@ref(fig:campaign)) 
In this section, equation represents a data set consisting of two variables: "campaign" and "duration." To analyze the relationship between these variables, a scatter plot is created, as shown (Figure \@ref(fig:campaign)). The scatter plot visually depicts the data points and their distribution. Analyzing the scatter plot helps to understand how the duration of the campaign relates to the different campaign stages represented by the values 5 to 0 and duration stages by the values 0 to 2000. It gives the data a visual representation, enabling a deeper comprehension of the campaign's development over time.


```{r campaign, fig.align='center', fig.cap='Scatter Plot: campaign VS. duration', results='asis', echo=FALSE}
survey %>%
  ggplot(aes(x = duration, y = campaign)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous("duration") +
  scale_y_continuous("campaign")
```


## Prediction

We employed a linear regression model to duration in  Marketing Campaign of Portuguese Banking Institution dataset,considering the independent factors campaign (C), cons.price.idx (CPI), and emp.var.rate (EVR). The model can be represented as follows:

\[ duration = \beta_0 + \beta_1campaign + \beta_2cons.price.idx + \beta_3emp.var.rate + \varepsilon \]

The coefficient \( \beta_0 \) represents the intercept or the baseline duration when all other predictor variables are zero. \( \beta_1 \), \( \beta_2 \), and \( \beta_3 \) are the coefficients associated with the campaign, consumer price index, and employment variation rate, respectively. This equation allows us to understand how changes in the campaign, consumer price index, and employment variation rate affect the duration of the outcome variable. By analyzing the coefficients, we can establish the strength and direction of the association between these variables and the duration. Understanding the effects of marketing initiatives and monetary considerations on the outcome of interest requires the use of this information.


## Results

(Figure \@ref(fig:predict))
By using this equation, we can estimate the predicted duration values for different sample points within the range of 0 to 500. The predictions are based on the correlation found between sample points and corresponding duration values found in the dataset. We may generalize from the observed samples by using the equation to generalize and estimate durations for new data points within the specified range. 

```{r predict, fig.align='center', fig.cap='Predicted duration VS. Actual duration', results='asis', echo=FALSE}
dataset <- read.csv("C:/Users/MSI/Desktop/20080946/data/Bank.csv")

model <- lm(duration ~  campaign + cons.price.idx +  emp.var.rate, data = dataset)


predictions <- predict(model, dataset)

plot(dataset$duration,
     type = "l", xlab = "Samples", ylab = "duration",
     col = "turquoise")

lines(predictions, col = "magenta")

legend("topright", legend = c("Actual", "Predicted"),
       col = c("turquoise", "magenta"), lty = 1, bty = "n")


```

# Conclusion

This academic paper explored the influence and effectiveness of marketing campaigns in a specific Portuguese banking institution. The research question focused on understanding how these campaigns shaped customer perceptions and preferences, as well as the factors contributing to their effectiveness. The analysis of the dataset, which comprised 149 observations and 21 variables, provided valuable insights into the marketing strategies employed by Portuguese banks. The results of the analysis provided valuable insights into the relationship between the predictor variables and the duration of marketing campaigns. The scatter plot depicted the progression of campaigns over time, allowing for a visual understanding of the relationship between campaign stages and duration stages. Furthermore, the predicted duration values based on the regression model provided estimates for new data points, enabling predictions beyond the observed samples. To sum up, this academic paper contributes to the existing knowledge on the role of marketing campaigns in Portuguese banking institutions. By investigating customer perceptions, preferences, and the factors influencing marketing effectiveness, the study provides insights that can guide future marketing strategies. The findings emphasize the importance of aligning campaigns with core values, leveraging both traditional and digital channels, and incorporating themes of financial literacy and corporate social responsibility. Ultimately, by understanding the factors that contribute to effective marketing campaigns, banking institutions can build strong customer relationships and establish themselves as trusted financial partners within the country.



\newpage

# References {#references}

::: {#refs}
:::
